Inverse energy transfer in three-dimensional quantum vortex flows

### 2025-06-24 revision/referee-response-2.tex

\refcomment{As recalled by the authors, inverse energy cascades show up when helicity symmetry is explicitely broken by external forcing as in [Plunian et al., JFM (2020)]. Their claim, then, is that vortex reconnection events in superfluid turbulence will similarly break helicity symmetry and trigger, in this way, an inverse energy cascade in the flow.}

The referee \red{correctly} understood \red{that}
the most important claim of our paper concerns the sign-defined helicity 
injection. We would like to highlight that we have consciously avoided 
talking about \red{an} {\it inverse energy cascade}, as we are well aware 
that our system is not turbulent. We have used the words {\it inverse energy transfer} instead.\\

\refcomment{While the paper’s idea is interesting and worth pursuing, I believe the authors fail to provide even minimal evidence to support their case. Below, I address my main points.
(i) First, the use of the word “turbulence” in the very first line (and used 16 times in other parts) of the manuscript is misleading: the flow studied by the authors is just a collision of vortex filaments. There is no turbulent flow at all here. It is all about a specific problem on superfluid flow instability.}

As the Referee is certainly aware, vortex reconnections play an important role in turbulence.We have never claimed that our system is turbulent, but we do think that our findings have a strong impact on quantum turbulence. In the text, we have only referred to `turbulence' in the introduction to motivate our work and to explain its relevance to a broad audience, and at the very end to comment on its implications in the conclusions. Explaining cascades, turbulence and invariants is necessary to understand the role of helicity on transfer towards large scales. We still believe that the use of the word turbulence is 
appropriate in our manuscript \red{to put our results into the most 
relevant context}.

@@

%
\begin{figure}[h!]
    \centering
    \includegraphics*[width=0.48\textwidth]{flux_wakes.png}
    \caption{Spectral normal fluid kinetic energy flux, $\Pi (k)$ for the wakes generated in the normal fluid, data from [arXiv:2501.08309].}.

\end{figure}

\refcomment{For the above reasons, I do not recommend the paper for publication in the PRL.}

\noindent \red{We trust} that we have clarified to the Referee the goal and main results of our Letter, and at the same time, provided enough arguments to emphasize the impact of our Letter.

### 2025-06-25 revision/cover_letter_REV.tex
Updated letter

% Sender Information
\begin{flushright}
    \begin{tabular}{l}
        \textbf{Piotr Stasiak} \\
        School of Mathematics, Statistics and Physics\\
        Newcastle University \\
        Newcastle  upon Tyne \\
        p.stasiak@newcastle.ac.uk \\
        \today
    \end{tabular}
\end{flushright}

@@

For Referee B, we believe that the referee has missed the main focus of the paper, which was to provide an explanation of the inverse energy transfer due to vortex reconnections in terms of a chiral imbalance of helical modes, and not to explain [Krstulovic\&Polanco PRL 2020], of which Krstulovic is a collaborator and co-author of this work. The paper by Krstulovic\&Polanco, fundamentally differs from ours in terms of the model used and the analysis, and we cite this work at the very end of our manuscript as a possible connection, and not as an explanation as the referees comments seem to suggest. We hope that we have made our comments sufficiently clear to the referee for the relevance of our work.

On behalf of the authors,

@@

\textbf{Piotr Stasiak}

\end{document}

>>>>

% Sender Information
% \begin{flushright}
%     \begin{tabular}{l}
%         \textbf{Piotr Stasiak} \\
%         School of Mathematics, Statistics and Physics\\
%         Newcastle University \\
%         Newcastle  upon Tyne \\
%         p.stasiak@newcastle.ac.uk \\
%         \today
%     \end{tabular}
% \end{flushright}

% \vspace{1cm}

@@

For Referee B, we believe that the referee has missed the main focus of the paper, which was to report an inverse energy transfer and provide an explanation due to vortex reconnections in terms of a chiral imbalance of helical modes, and not to explain [Krstulovic\&Polanco PRL 2020]. We cite this work in the very last paragraph of our Letter to establish a possible connection; our findings are not at all an explanation of it. The paper by Krstulovic\&Polanco, fundamentally differs from ours in terms of the model used and the analysis. We hope that the main aim of the paper is now clear to the referee and we hope that they can see the relevance of our work.

@@

\textbf{Piotr Stasiak}\\
\textbf{Andrew Baggaley}\\
\textbf{Carlo Barenghi}\\
\textbf{Giorgio Krstulovic}\\
\textbf{Luca Galantucci}\\
\end{document}
